Synchronizing Distributed Openflow Controllers\\{\Large Toward More Powerful In-Band Synchronization Objects

### 2015-03-11 inband-STN.tex

\begin{algorithm}[t]
    \caption{$\textit{cond-add}(x)$}
    \label{alg:multi-add}
    \begin{algorithmic}[1]
    \Require id $i$, unique constrain (defaults to \texttt{false}) $b\_unique$, caller id $caller$ (defaults to \emph{self}).
%    \Ensure
    		\State $value \gets i\concat i$
    		\State $mask \gets caller\concat all-1$
    		\State $cookie \gets i\concat caller$
    		\State $action \gets i\concat caller$
    		\If {$b\_unique$}
    			\State $flag \gets 0$
    		\Else
    		    \State $flag \gets CHECK\_OVERLAP$
    		\EndIf
    					\State $cmd\gets \textsc{FlowMod}(match=(value,mask), operation = ADD, cookie, flag, action) $
			\Return $cmd$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{$\textit{cond-delete}(x)$}
    \label{alg:template}
    \begin{algorithmic}[1]
    \Require id $i$, unique constrain (defaults to \texttt{false}) $b\_unique$, caller id $caller$.
%    \Ensure
    		\State $value \gets i\concat i$
    		\State $mask \gets caller\concat all-1$
    		\State $cookie \gets i\concat caller$
    		\If {$b\_unique$}
    			\State $cmd\gets \textsc{FlowMod}(match=(value,mask), operation=DELETE) $
    		\Else
    		    \State $cmd\gets \textsc{FlowMod}(match=(value,mask), operation=DELETE\_STRICT, cookie) $
    		\EndIf

@@

\begin{algorithm}[t]
    \caption{$\textit{add}(x)$}
    \label{alg:add}
    \begin{algorithmic}[1]
    \Require  id $i$.
%    \Ensure
    		\State $command \gets OFPGC\_ADD$
    		\State $type \gets OFPGT\_INDIRECT$
    		\State $group\_id \gets i$
    		\State $buckets \gets [dummy\_backet]$
    		\State $cmd\gets GroupMod(command, type, group\_id, buckets) $
			\Return $cmd$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{$\textit{delete}(x)$}
    \label{alg:delete}
    \begin{algorithmic}[1]
    \Require id $i$, unique constrain (defaults to False) $b\_unique$, caller id $caller$.
%    \Ensure
    		\State $command \gets OFPGC\_DELETE$
    		\State $group\_id \gets i$
    		\State $cmd\gets GroupMod(command, group\_id) $
			\Return $cmd$
    \end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}[t]
    \caption{$\textit{claim}(x)$}
    \label{alg:multi-add}
    \begin{algorithmic}[1]
    \Require \emph{self} as the calling controller id.
%    \Ensure
    		\State $value \gets x\concat x$
    		\State $mask \gets self\concat all-1$
	    	\State $match \gets (value,mask)$
    		%\State $cookie \gets x\concat self$
    		\State $action \gets x\concat self$
    		\State $flag \gets 0$
    		\State $cmd\gets \textsc{FlowMod}(match, op = ADD, flag, action) $
			\Return $cmd$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{$\textit{check}(x)$}
    \label{alg:multi-add}
    \begin{algorithmic}[1]
    \Require \emph{self} as the calling controller id.
%    \Ensure
    		\State $value \gets x\concat x$
    		\State $mask \gets self\concat all-1$
    		\State $match \gets (value,mask)$
    		%\State $cookie \gets x\concat self$
    		\State $action \gets x\concat self$
    		\State $flag \gets CHECK\_OVERLAP$
    		\State $cmd1\gets \textsc{FlowMod}(match, op = ADD, flag, action) $
    		\State $cmd2\gets \textsc{FlowMod}(match, op = DELETE) $
			\Return $cmd1$,$cmd2$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{$\textit{unclaim}(x)$}
    \label{alg:template}
    \begin{algorithmic}[1]
    \Require \emph{self} as the calling controller id.
%    \Ensure
    		\State $value \gets x\concat x$
    		\State $mask \gets self\concat all-1$
    		%\State $cookie \gets x\concat self$
    		\State $match \gets (value,mask)$
    		\State $cmd\gets \textsc{FlowMod}(match, op=DELETE, cookie) $

@@

\begin{algorithm}[t]
    \caption{$\textit{compare\&set}(old,new)$}
    \label{alg:add}
    \begin{algorithmic}[1]
    %\Require  id $i$.
%    \Ensure

    		\State $op \gets OFPGC\_DELETE$
    		\State $group\_id \gets old$
    		\State $cmd1\gets GroupMod(op, group\_id) $

    		\State $op \gets OFPGC\_ADD$
    		\State $type \gets OFPGT\_INDIRECT$
    		\State $group\_id \gets new$
    		\State $buckets \gets [dummy\_backet]$
    		\State $cmd2\gets GroupMod(op, type, group\_id, buckets) $
			\Return $cmd1,cmd2$
    \end{algorithmic}
\end{algorithm}
